Different forms of uncertainty differently affect the evolution of social learning

### 2022-10-10 meanNetPayoffs.tex
edited model and analysis

    \begin{center}
      {\Huge \textbf{+} \huge Location where homogenous social and asocial payoffs
      are equal} \quad \quad 
    \end{center}

>>>>

    \begin{center}
       \includegraphics[width=1.85in]{Figures/legendElements/dot.pdf}
       {\huge Average all-social population payoffs}  \\[1.125em]
       \includegraphics[width=1.85in]{Figures/legendElements/ldash.pdf} 
       {\huge Average all-asocial population payoffs} \\[1.125em]
       \includegraphics[width=1.85in]{Figures/legendElements/solid.pdf} 
       {\huge Simulated average population payoffs} \\[1.125em]
      {\Huge \textbf{+} \huge $u$ value where homogenous social and asocial payoffs
      are equal} 
    \end{center}
